Figures

### 2020-02-21 figures/00_maps.Rmd
adjust figure dimensions

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
  # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
  # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_point_rast(data = dt_notsf, aes(x = X, y = Y, color = maxdepth_class), 
                    size = 0.3, alpha = 0) +
    scale_color_manual(values = viridisLite::viridis(5)) +
    geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m < 10), 
            aes(x = X, y = Y, color = maxdepth_class), size = 0.3, alpha = 0.8) +
    geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m > 10), 
            aes(x = X, y = Y, color = maxdepth_class), size = 0.3, alpha = 0.8) +
    labs(color = "Max depth (m)") +
    coord_sf(datum =  NA) +
    theme_void()

@@

```{r gg_reservoir, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt           <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  distinct(lagoslakeid, .keep_all = TRUE)
dt_withres <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  dplyr::distinct(lagoslakeid, reservoir_class) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt           <- inner_join(dt, dt_withres) %>%
  arrange(desc(reservoir_class))

>>>>

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
  # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
  # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_point_rast(data = dt_notsf, aes(x = X, y = Y, color = maxdepth_class), 
                    alpha = 0) +
    scale_color_manual(values = viridisLite::viridis(5)) +
    geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m < 10), 
            aes(x = X, y = Y, color = maxdepth_class), size = 0.2, alpha = 0.8) +
    geom_point_rast(data = dplyr::filter(dt_notsf, lake_maxdepth_m > 10), 
            aes(x = X, y = Y, color = maxdepth_class), size = 0.2, alpha = 0.8) +
    labs(color = "Max depth (m)") +
    coord_sf(datum =  NA) +
    theme_void()

@@

```{r gg_reservoir, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt           <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  distinct(lagoslakeid, .keep_all = TRUE)
dt_withres <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::distinct(lagoslakeid, reservoir_class) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt           <- inner_join(dt, dt_withres) %>%
  arrange(desc(reservoir_class))

### 2020-02-21 figures/01_geometry.Rmd
adjust figure dimensions

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

@@

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5}
theme_opts <- theme(legend.position = "none")

>>>>

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) + 
  geom_point() +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

@@

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5, fig.height=4.2}
theme_opts <- theme(legend.position = "none")

### 2020-02-21 manuscript/figures.Rmd
adjust figure dimensions

![Diagram showing the assumption of most lake depth models that the nearshore slope is extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=85%}

![Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)](../figures/lake_shape.pdf){width=85%}

>>>>

![Diagram showing the assumption of most lake depth models that the nearshore slope is extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=80%}

![Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)](../figures/lake_shape.pdf){width=80%}
